Probabilistic Audio Localization in Wireless Acoustic Sensor Networks

### 2016-05-10 paper/paper.tex
PRM Star in latex done
paper changes

@@

\begin{algorithm}[ht] 
    \caption{Multiple Source Sound Localization}
    \label{algo:MS}
    \begin{algorithmic}[1]
        \setcounter{ALC@line}{0}
        \vspace*{1mm}

>>>>

The Probabilistic RoadMap algorithm has two phases: the preprocessing phase in which a roadmap is constructed by sampling random points in the C-space, and the query phase in which a graph search over the roadmap is made to connect initial and goal configurations.The map is constructed during the preprocessing phase by sampling random points in the C-space and then adding them to the nearest existing vertices in the roadmap. in

@@

\begin{algorithm}[ht] 
    \caption{PRM*}
    \label{algo:PRMstar}
    \begin{algorithmic}[1]
        \setcounter{ALC@line}{0}
        \vspace*{1mm}
